---
title: "Example Covid Report"
author: "INFO-201: Class Demo"
date: "2/7/2022"
output: html_document
---

```{r setup, include=FALSE}
source("../source/analysis.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Covid Report
In the analysis file, we were able to examine a data set that included national data regarding covid cases and deaths on particular dates. I used the 'get_total_cases()' function to get the total number of cases and found that there was 97,654,808 total cases. I used the 'get_total_deaths()' function to get total deaths and found that there was 1,069,792 total deaths.


(**Note**: Why are there no commas in the *total number of US deaths* ? Can you change `analysis.R` file so that the number is commented with commas?)
The total number of US deaths originally did not have commas because the prettyNum() function was not origianlly included. After I used that function in the 'get_total_deaths' function, I got the output to include commas.

I also want to show the chart:
``` {r echo=FALSE}
cases_plot
```

